---
title: "The Darkened Band"
author: "Austin Meyer"
date: "3/20/2019"
output: ioslides_presentation
css: styles.css
smaller: true
runtime: shiny
widescreen: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

# Initial presentation

## Initial presentation

- <font size="5">59 yo female with morbid obesity, chronic vertigo, hypertension, and a recent episode of necrotizing fasciitis to the mons pubis. She presented as a transfer from SNF for hypotension.</font>

> - <font size="4">Since her hospitalization at OSUE she had been in a SNF recovering. She was having chronic diarrhea and poor PO intake which was worse over the past week with frequent NBNB emesis and watery diarrhea.</font>

> - <font size="4">Routine vitals done at SNF. She was hypotensive to 80s systolic. She was seen at MCH where she was still hypotensive (lowest 79/46), and was reportedly febrile. She was bolused 2L NS and started on phenylephrine. There was concern for UTI based on urinalysis (had indwelling foley, last changed 1 week prior) and was started on Cefepime. Labs significant for AKI and troponin.</font>

> - <font size="5">On arrival, the patient reported some nausea and then had a somewhat bilious emesis. Denied symptoms other than normal vertigo.</font>

# Differential?

## Vitals on arrival

BP = 107/67<br><br>
HR = 106<br><br>
SpO2 = 95% on RA<br><br>
RR = 26<br><br>
Temp = 99.3<br><br>
Drips = phenyleprine at 0.5 mcg/kg/min

## Physical exam

- AOx4, No distress, Overweight, Laying in bed
- Cardiopulmonary exam was wnl
- Mild epigastric tenderness
- Foley in place
<br><br><br><br>
- Site of prior debridement of left groin with healthy granulation tissue. 
- I&D site on right lower abdomen with packing in place without drainage. 
- Over the right upper abdomen there are clusters of vesicles that appear to be crusted over in the region of T6 dermatome on the right. 

# Things to order?

## Initial labs

- Na 141, K 4.6, Cl 110, HCO3 17, Cr 1.2<br><br>
- LFTs wnl<br><br>
- Trop 0.4<br><br>
- WBC 9.6, Hgb 11.8, Plt 341<br><br>
- Lactate 1.4

## Imaging

- Chest xr: 
<font size="4"><br>Life support devices as described above. No acute cardiopulmonary findings.</font>

- CT A/P: <br>
<font size="4">1.) Previously described ill-defined region of stranding and gas within the perineum is nonvisualized on today's exam, likely out of the field-of-view <br>
2.) Multiple nonspecific prominent para-aortic, pelvic sidewall, and inguinal lymph nodes are stable-slightly decreased in size from the prior exam. <br>
3.) Cholelithiasis. No specific evidence of acute cholecystitis. <br>
4.) Multiple bilateral hyperdense renal cystic lesions, some of which are new from the prior exam. These are incompletely characterized and may represent hemorrhagic/proteinaceous cysts. Underlying renal neoplasia cannot be excluded on this exam. <br>
5.) Circumferential urinary bladder wall thickening may in part be related to underdistention. Consider correlation with urinalysis to exclude acute cystitis. <br></font>

## Updates and what was done...

> - Became a bit hypotensive so bolused 1L and phenylephrine increased to 1 mcg/kg/min<br><br>
> - Started on broad antibiotics including dapto, cefepime, flagyl, acyclovir<br><br>
> - After one dose of cefepime and flagyl, switched to merrem<br><br>
> - After one dose of acyclovir switched to valtrex<br><br>
> - Temp increased to 100.3 overnight

# Day one 

## Day one update

> - NAE, still on phenylephrine at stable dose<br><br>

> - Phenylephrine quickly weaned off in the morning and pt went hypotensive <br>__Started on levophed__

> - Vitals: <br>&nbsp;&nbsp;- HR 101 <br>&nbsp;&nbsp;- MAPs consistently around 65 <br>&nbsp;&nbsp;- RR 18-24 <br>&nbsp;&nbsp;- Temp 100.2 <br>&nbsp;&nbsp;- RA 

> - Exam: AOx4, NAD, Seems completely fine, Eating normally

## More information from prior hospitalization

- __Candida glabrata__ at high CFU in urine<br><br>
- __Lactobacillus gasseri__ on anaerobic of mons pubis wound<br><br>
- __Candida glabrata__ on fungal of mons pubis wound<br><br>
- Various __ESBL bugs__ on standard culture of mons pubis wound

## Day one labs

- Na 142, K 4.2, Cl 111, HCO3 19, Cr 1.1
- Trop peaked at 0.42
- WBC 13.4 w/ left shift, Hgb 11.3, Plt 390
- Lactate 1.8 -> 2.0 -> 1.4
<br><br>
- POC flu negative
- Procal 0.09, CRP 13.3, ESR 11
- UA off exchanged foley: <br>&nbsp;&nbsp;- Turbid, Large Blood, >20 WBCs, Small LE, Nitrites negative

# Refine differential, orders?

# Day two

## Day two update

- NAE, levophed weaned to 0.02 mg/kg/min overnight

> - Levophed requirement increased back to 0.08 mg/kg/min

> - Vitals: <br>&nbsp;&nbsp;- HR 95 <br>&nbsp;&nbsp;- MAPs are variable <br>&nbsp;&nbsp;- RR 20-33 <br>&nbsp;&nbsp;- Temp 98 <br>&nbsp;&nbsp;- SpO2 92% on RA 

> - Exam: AOx4, NAD, Still completely fine

> - Management: Started pt on caspofungin for Candida on last admission

## Day two labs

- Na 137, K 4.0, Cl 111, HCO3 18, Cr 0.99<br><br>
- Trop stopped prior day<br><br>
- WBC 9, Hgb 9.8, Plt 318<br><br>
- Lactate stopped prior day<br><br>
- Blood cx: NGTD

# Refine differential, orders?

# Day three

## Day three updates

> - NAE, levophed stable at about 0.1 mg/kg/min, unable to wean<br><br>
> - Vitals: Unchanged<br><br>
> - Drips: Still requiring 0.07 mcg/kg/min to maintain MAPs > 65<br><br>
> - Exam: AOx4, NAD, Still completely fine

## Day three labs

- Na 138, K 3.7, Cl 111, HCO3 18, Cr 0.84<br><br>
- WBC 7.6, Hgb 9.4, Plt 297<br><br>
- Blood cx: NGTD

# Final thoughts?

## New imaging

> - TTE: <font size="4"><br>&nbsp;&nbsp;Overall image quality is good. Tachycardic during exam. <br>&nbsp;&nbsp;The LV chamber size is small, partially compressed by the RV. <br>&nbsp;&nbsp;Systolic function is hyperdynamic, EF >70% <br>&nbsp;&nbsp;The right ventricle is severely enlarged (RV : LV ratio is 1.5-2 : 1). <br>&nbsp;&nbsp;There is severe RV dysfunction.  <br>&nbsp;&nbsp;Septal motion is consistent with right ventricular pressure and volume overload. <br>&nbsp;&nbsp;There is free wall hypokinesis. <br>&nbsp;&nbsp;There is mild-to-moderate tricuspid regurgitation <br>&nbsp;&nbsp;There is aortic sclerosis without stenosis. <br>&nbsp;&nbsp;Moderately elevated pulmonary pressures, estimated RVSP 60-65 mmHg. <br>&nbsp;&nbsp;Small pericardial effusion without echocardiographic evidence of tamponade. <br>&nbsp;&nbsp;No evidence of right to left shunt by saline bubble study.</font>

##

```{r out.width = "65%", fig.align="center"}
library(knitr)    # For knitting document and include_graphics function
library(ggplot2)  # For plotting
library(png)      # For grabbing the dimensions of png files

img1_path <- "figures/PE_1.png"
include_graphics(img1_path)
```

##

```{r out.width = "65%", fig.align="center"}
library(knitr)    # For knitting document and include_graphics function
library(ggplot2)  # For plotting
library(png)      # For grabbing the dimensions of png files

img1_path <- "figures/PE_2.png"
include_graphics(img1_path)
```

##

```{r out.width = "60%", fig.align="center"}
library(knitr)    # For knitting document and include_graphics function
library(ggplot2)  # For plotting
library(png)      # For grabbing the dimensions of png files

img1_path <- "figures/PE_3.png"
include_graphics(img1_path)
```

## 

```{r out.width = "55%", fig.align="center"}
library(knitr)    # For knitting document and include_graphics function
library(ggplot2)  # For plotting
library(png)      # For grabbing the dimensions of png files

img1_path <- "figures/PE_4.png"
include_graphics(img1_path)
```

# Final Dx: Massive PE

# So... what happened here?

##

<p style="text-align:center">
<object type="image/svg+xml" data="figures/Cognitive_bias_codex_en.svg" height="500px">
<!-- Your fall back here -->
<img src="figures/Cognitive_bias_codex_en.svg" height="500px"/>
</object>
</p>

# Teaching part

## Epidemiology

## Diagnosis

## Treatment

## Probability of pulmonary embolism

```{r wells}
library(tibble)
library(ggplot2)
library(shinyWidgets)

fluidPage(
  fluidRow(
    column(5,
           checkboxGroupButtons("wells", label = h3("Wells Criteria", style = 'line-height: 0'),
                                direction = 'vertical',
                                choices = list("Clinical signs or symptoms of DVT" = 3, 
                                               "PE is #1 diagnosis" = 3, 
                                               "Heart rate > 100" = 1.5,
                                               "Immobilization >= 3 days or surgery in last 4 weeks" = 1.5, 
                                               "Previous objective PE or DVT" = 1.5, 
                                               "Hemoptysis" = 1,
                                               "Cancer and treatment in last 6 months" = 1
                                ),
                                selected = 0),
           hr(),
           radioGroupButtons("ddimer", label = h3("D-dimer > 500 µg/L", style = 'line-height: 0'), 
                             choices = list('Yes' = 'positive', 'No' = 'negative', 'Not available' = 'NA'),
                             selected = 'NA')
    ),
    
    column(7,
           plotOutput('probPlot', width="500px", height="410px"), 
           textOutput('probText'),  
           align = 'right')
  )
)


output$probText <- renderText({
  points <- sum(as.numeric(input$wells))
  prob <- if(points < 3) 0.06 else if( points < 7 ) 0.23 else 0.49
  
  lr <- if(input$ddimer == 'NA') 1 else if(input$ddimer == 'positive') 0.91 / (1 - 0.6) else if(input$ddimer == 'negative') (1 - 0.91) / 0.6
  
  posttest.odds <- prob / (1 - prob) * lr
  posttest.prob <- round(posttest.odds / (1 + posttest.odds) * 100, 2)
  
  paste('Probability of PE = ', posttest.prob, '%', sep = '')
})

output$probPlot <- renderPlot({
  points <- sum(as.numeric(input$wells))
  prob <- if(points < 3) 0.06 else if( points < 7 ) 0.23 else 0.49
  
  lr <- if(input$ddimer == 'NA') 1 else if(input$ddimer == 'positive') 0.90 / (1 - 0.45) else if(input$ddimer == 'negative') (1 - 0.95) / 0.65
  
  posttest.odds <- prob / (1 - prob) * lr
  posttest.prob <- posttest.odds / (1 + posttest.odds)
  
  df <- tibble(x = factor(c('Pretest', 'Posttest'), levels = c('Pretest', 'Posttest')), y = c(prob, posttest.prob))
  
  ggplot(df, aes(x = x, y = y)) + geom_bar(stat = 'identity') + 
    labs(x = '', y = '') +
    theme_classic() + 
    ylim(0,1) + 
    ylab('Fractional Probability') +
    theme(plot.margin = unit(c(0,0,-0.5,0), "lines"))
  #gg2 <- ggplot_gtable(ggplot_build(p))
  #gg2$layout$clip[gg2$layout$name == "panel"] <- "off"
  #grid.draw(gg2)
})

```


<font size="1">Ceriani E, et al. Clinical prediction rules for pulmonary embolism: a systematic review and meta‐analysis. Journal of thrombosis and haemostasis. 2010, 8:957-70.</font><br>
<font size="1">Crawford F, et al. D‐dimer test for excluding the diagnosis of pulmonary embolism. Cochrane Database of Systematic Reviews. 2016, 8.</font>

